\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

Health is the most important thing we have in our lives.
If we want to be healthy we need to, among other things, think about what we eat.
People today are trying various diets in order to stay in shape and feel good.
There are also many people who suffer from food allergies who need to pick carefully what they eat, as some food is harmful to them. 

In the European Union, there exist laws which make it mandatory for restaurants to inform guests about allergens in served meals. Typicaly, this resolves in a menu containing a list of allergens within the description of each meal. Another option for a restaurant is to create a numbered list of allergens and use numbers instead of labels, which makes the menu more concise but also not very pleasant to decode.

If a person who is on a diet or has an allergy decides to visit a restaurant which they have never been to, they spend a lot of time browsing the restaurant's menu as it can often be hard to choose a meal which is healthy for them to eat.

In this thesis we will document the process of the creation of a web application whose purpose will be to help these people to be able to quickly choose what they want to eat at a restaurant. 
The application will achieve this by letting its users create their personal profile and within it to specify what allergies they have or what diets they are on. Moreover, the user will be able to specify their overall food preferences, as to make the application also useful for people who are not on a diet nor have food allergies.
Another goal of the application will be to enable restaurant providers create their menus online. 
Then, when a visitor will browse a restaurant's menu using the application, it will make it possible to only display those meals which the visitor is able or willing to eat according to their profile.

Also, we need to be aware that whether someone is on a diet or has an allergy are personal information which the user may be sensitive about.

We will therefor design and implement the application in a safe and modern way which will ensure that only the user can view and manipulate with their personal profile data. This will be accomplished by using a technology called Solid which provides users with Solid pods --- their personal data storage units.
